The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl

### 2018-02-02 suppinfo.tex
feb 2 (version sent to co-authors)
Changes made by Denis, new figures for SI, text changed.

\author{Ch. Nicolas}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Wandared Pokapanich}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Th. Saisopa}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{P. Songsiriritthigul}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Y. Rattanachai}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
  {The electronic structure of aqueous KCl revealed by X-ray absorption and Auger electron spectroscopy
\\  
  The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$. The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
\label{fg:rad_dens}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=1.0]{figures/rad_dens_kcl.eps}
\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel). The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
\label{fg:rdens_ions}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliography{F:/Articles/biblography/Bibliography}

>>>>

\author{Christophe Nicolas}
\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}

\author{Wandared Pokapanich}
\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000 Thailand}

\author{Th. Saisopa}
\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}

\author{P. Songsiriritthigul}
\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}

\author{Y. Rattanachai}
\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}

@@

\author{Ralph P\"{u}ttner}
\affiliation{Fachbereich Physik, Freie Universit\"at Berlin, Arnimallee 14, D-14195, Berlin, Germany}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
  {The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl}

@@

%\begin{figure}
%\centering
%\includegraphics[scale=0.3]{figures/fg2_k_6w_okxx_55_rad_dens.eps}
%\caption{Radial density distributions of the singly-occupied natural orbitals occupied by the excited electron in the core excited states 3609.11\,eV (1\,$^{1}$A$_{2}$), 3609.41\,eV (2\,$^{1}$E) and 3609.64\,eV (3\,$^{1}$E) of K$^{+}$(H$_2$O)$_6$. The grey line at 2.816\,\AA~represents the equilibrium K-O distance.}
%\label{fg:rad_dens}
%\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{figures/rad_dens_kcl.eps}
\caption{Radial density distributions of the singly-occupied natural orbital occupied by the excited electron corresponding to the 1s$\rightarrow$4p, 1s$\rightarrow$3d and 1s$\rightarrow$5p core excitations in \ki~(lower panel) and \cli~(upper panel). The insets show the region of distances relevant for the overlap with the 1s core orbital whose radial density is shown as a grey shaded area.}
\label{fg:si_rdens_ions}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}. The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step. From these curves we determine the charge transfer time $\tau_{\texttt{CT}}$ according to the formula $\tau_{\texttt{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.  The green line defines the Cl$^{-}_{\texttt{aq}}$(1s) ionization potential.}
\label{fg:si_ct_time}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{F:/Articles/bibliography/Bibliography}
%\bibliography{Bibliography}
